\section{Reflection}
% Reflect on the societal relevance and/or ethical implications of your proposed research, where you may consider the following questions:
% \begin{itemize}
%     \item What is the societal relevance of your research? 
%     \item Can the research be built upon? 
%     \item Is there a direct potential harm to the environment, society or are there economic implications of the research when used as it is intended? 
%     \item Can you foresee the research being used for unintended purposes with potential environmental, societal, cultural, or economic consequences? 
% \end{itemize} 

% As a responsible researcher, you should be aware of the risks that may come with your research, and requires you to forecast not only the near-term, but also the long-term cost and values of your work. When it comes to social responsibility, you should be aware of social and cultural implications related to materials use (e.g., land changes, water use and pollution, labor rights, etc.) which may be impacted by the outcomes of your research. Also, you should be aware of and understand the ethical implications that may come with your work.
The societal relevance of this project is already discussed at the start of section 1. Also, no direct potential harm to the environment or society is present in this project or for other unintended, unforeseen purposes. This research will kickstart a larger, more ambitious project called Mass Balance Machine. Once there is a model that can estimate the mass balance for glaciers in Norway and the other regions of interest, the next step is to make it so that the model can estimate glacier mass balances all around the globe. This will also be useful for glaciologists researching glaciers that have not been studied before. 

Some ethical implications must be considered in this study. One of them is cherry-picking the results. The model can be biased and only make good predictions for distinctive cases, while other predictions are far off. Suppose only the results for these distinctive cases are exhibited in the results. In that case, the wrong message about the model performance is conveyed, similarly, for the uncertainty quantification presented by the results. One can only give a fair judgement if all the results are presented. Lastly, the model and its decisions must be somewhat insightful and explainable rather than a complete black box. With a custom loss-function and feature importance, this problem can be alleviated. 
